Nuclei Segmentation in Histopathology images using Deep Neural Networks

### 2016-11-06 Paper.tex
Introduction is finished

% Template for ISBI-2016 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,graphicx}
\usepackage{amsfonts}
\usepackage[utf8]{inputenc}
\usepackage[francais]{babel}

@@

% segmentation is the bottleneck of cellular phenotyping in cancer
% tissues. 
In this latter case, one of the essential steps is to
segment nuclei from tissue images in order to be able to
assign them a cell type or phenotypic label and to evaluate their
spatial distribution. We concentrate on nuclei, as they are indicative
of many cellular phenotypes\citep{Chow2012}, and their morphology is 
currently used by pathologists in order to
identify the mitotic index and the level of nuclear pleomorphism

Regarding cellular phenotyping, we will focus on nuclear morphologies,
because (1) nuclei are indicative of many cellular phenotypes20, (2)
their morphology is currently used by pathologists in order to
identify the mitotic index and the level of nuclear pleomorphism12 and
(3) their segmentation is feasible5 in contrast to many other cellular
structures, such as the plasma membrane for instance.

Yet, segmentation of nuclei is a
complicated task: tissue type, staining differences and cell type
convey them different visual characteristics, which makes it very difficult to
design traditional image segmentation algorithms that work
satisfactorily for all of these different cases. On the other hand,
deep learning algorithms have been recently used

% motivation of the deep learning approach (for instance by taking
% fewer samples). t

of bioinformatics programs aiming at

related to cancer and they
have revolutionized our understanding of the molecular basis of cancer
and led to the definition of clinically relevant subtypes, bearing
high potential for the development of new cancer therapies.

@@

% References should be produced using the bibtex program from suitable
% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
% style file from IEEE produces unsorted bibliography list.
% -------------------------------------------------------------------------
\bibliographystyle{IEEEbib}
\bibliography{strings,refs}

>>>>

% Template for ISBI-2016 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,graphicx}
\usepackage{amsfonts}
\usepackage[utf8]{inputenc}
\usepackage[francais]{babel}
\usepackage{hyperref}

@@

% segmentation is the bottleneck of cellular phenotyping in cancer
% tissues. 
In this latter case, one of the essential steps is to
segment nuclei from tissue images in order to be able to
assign them a cell type or phenotypic label and to evaluate their
spatial distribution. We concentrate on nuclei, as they are indicative
of many cellular phenotypes\cite{Chow2012}, and their morphology is 
currently used by pathologists in order to
identify the mitotic index and the level of nuclear
pleomorphism\cite{Elston1991}.

Yet, segmentation of nuclei is a
complicated task: tissue type, staining differences and cell type
convey them different visual characteristics, which makes it very difficult to
design traditional image segmentation algorithms that work
satisfactorily for all of these different cases. On the other hand,
deep learning algorithms have been used recently with great success to
complex segmentation tasks in biology\cite{Ciresan2012,Ronneberger2015}.

The contribution of this paper is three-fold: (1) we have generated a
ground truth of annotated images containing segmentation results for
more than 2000 cells. The dataset can be used by the scientific
community. (2) We apply a deep neural network end-to-end strategy and
demonstrate the superiority of this approach with respect to
previously proposed simpler architectures. (3) We propose a
post-processing strategy of the posterior probabilities provided by
the network. This post-processing strategy is based on mathematical
morphology and has a rigorous interpretation as to when objects are to
be split.

@@

% References should be produced using the bibtex program from suitable
% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
% style file from IEEE produces unsorted bibliography list.
% -------------------------------------------------------------------------
\bibliographystyle{IEEEbib}
\bibliography{strings}
